### 2022-01-17 response2/response2.tex
Add res to q2

>>>>

\subsubsection*{Comment 2 -
\color{RoyalBlue} Moreover, the authors are misinterpreting the results of earlier theoretical works. In particular, Ref. [31] demonstrates both the effect of photo excitations of electrons and the dressing of electronic states.}

We thank the reviewer for mention this deficiency. We believe this comment from the reviewer comes mainly from our statement “Lately, several experimental [50–53] and theoreti- cal [54–57] studies have uncovered various remarkable magneto-transport properties induced by microwave radiation on 2DEG quantum Hall systems. However, these experiments and theoretical models only analyzed the behavior of MIROs in 2DEG systems which are based on photon absorption from the applied low-frequency field. It is important to state that the difference between our SdH oscillations and MIROs [50–53] by considering the frequency range of the applied electromagnetic field.” in the Section IV (page 9) in the manuscript. On a re-reading the manuscript, we see that the language we had used here is ambiguous and admit that the statement gives a meaning that is quite different to what we were trying to convey.

What we meant to say here is that, once TM is fixed to the particular value we use in the simulations (i.e TM = TR), we can neglect the bath BM afterwards when analysing how the optical field affects the heat flows within the system. We never meant to say that the bath BM should be removed from the system at the beginning.
